### 2014-01-17 thesis/src/chapters/chapter-adaptivity.tex
Thesis: renamed chapter

\chapterintro{This chapter introduces concepts and mechanisms that enhance a platform with adaptivity capabilities, which are often achieved by fusion of rules, policies and scaling techniques.}

\section{Introduction}
In short, platform adaptivity adds a auto-scaling features to a solution offered by Platform-as-a-Service provider. Key concept is to have a Elasticity Controller which gathers probes from virtual machines and uses that knowledge to execute appropriate action on cloud instance, indirectly modifying consecutive probes \cite{VaRoBu11}. This concept illustrates diagram \ref{ch3:elasticity-controller}.

>>>>

\chapterintro{This chapter introduces concepts and mechanisms that enhance a platform with adaptivity capabilities achieved by a fusion of rules, policies and scaling techniques.}

\section{Introduction}
What makes a concept of an adaptivity enticing is crucial idea behind guaranteeing Quality-of-Serivce: automatization. Generally, ensuring and enforcing given quality can be seen as continuous monitoring an reacting to events when necessary. Such idea can be expressed as following IT process:

While system administrator can be directly responsible for manually performing above-mentioned steps, it is much more favourable to automatize this process leading to system self-adaptation. Not only does it lead to efficiency of an IT process but also to its effectiveness \cite{IBM06}. It is possible through:
\begin{itemize}
  \item \emph{rapid process initiation} - components auto-initiates actions based on information derived from a system
  \item \emph{reduced time and skill requirements} - automatization of IT processes makes them easier and less troublesome what is especially important for skill-intensive, error-prone and long lasting tasks
\end{itemize}

In a context of delivering a computing platform, adaptivity adds auto-scaling features to a solution offered by Platform-as-a-Service provider. Self-managing is possible through usage of an Elasticity Controller which gathers probes from resource such as application container and uses that knowledge to execute appropriate action on that resource, indirectly modifying consecutive probes \cite{VaRoBu11}. This concept illustrates diagram \ref{ch3:elasticity-controller}.

### 2014-01-17 thesis/src/chapters/chapter-introduction.tex
Thesis: renamed chapter

\section{Motivation}
One of the keys factors that has driven transformation of computing industry in the last years is the perception of computing utilities as an ordinary property, which can be easily accessed and adjusted to a specific needs. That point of view resulted in profusion of different services, often collectively referred as a cloud computing \cite{MeGr11}. Similarly to services common to traditional markets, customers expect them to be accessible on demand and in easy manner, while paying only for the consumed goods. Furthermore, customers are interested in a given service provider only when it is eligible to guarantee appropriate quality of service.

@@

While autonomic computing has a long history, it has not been directly applied to a multi-layered problem that exists in a cloud computing environment. Especially, the research area at the last layer, which sizes across different service providers, is new. Although, architecture known as InterCloud investigates problem of cooperation and negotiation at cloud level, it neither has been implemented nor presented in context of autonomic system.

\subsection{Business}
The rapid growth of interest in cloud computing in recent years resulted in huge sums of money being invested in the field. Figure \ref{ch1:public-cloud-services-market-size} shows the size of the public cloud services market in 2012 and the forecast of its nearly two times growth in 2016. This data suggests that the subject is attractive for IT industry from the economic point of view. However, higher amounts of money spent on cloud services involve higher expectations of theirs quality from customers. Although the most significant players in cloud computing have been in the field for quite a long time, it is still possible to outline some deficiencies their products have. Additionally, lack of common standards hinder cooperation among different cloud providers. For example it is nearly impossible to create an autoscaling cloud federation with Amazon Web Services (current leader in providing cloud services\cite{GartnerMagicQuadrantSep2013}) and another provider. What is more, Amazon AWS users cannot use more lightweight virtualization methods, such as linux containers. Nevertheless, when compared to other companies especially in terms of autoscaling capabilities, Amazon really shines. OpenShift, RedHat PaaS solution, ensures application scaling but with very limited possibilities of customisation of the process -- the user can only choose if their application should scale and the whole algorithm is solely based on the number of concurrent requests to the application. Users of Heroku, another PaaS solution, have no automation tool that would control the number of instances (\emph{dynos} in Heroku nomenclature) their application is running on -- they can change it manually.

>>>>

\section{Motivation}
One of the keys factors that has driven transformation of computing industry in the last years is the perception of computing utilities as an ordinary property\cite{BuYeVeBrBr09}, which can be easily accessed and adjusted to a specific needs. That point of view resulted in profusion of different services, often collectively referred as a cloud computing \cite{MeGr11}. Similarly to services common to traditional markets, customers expect them to be accessible on demand and in easy manner, while paying only for the consumed goods. Furthermore, customers are interested in a given service provider only when it is eligible to guarantee appropriate quality of service.

@@

While autonomic computing has a long history \cite{Mu04}, it has not been directly applied to a multi-layered problem that exists in a cloud computing environment. Especially, the research area at the last layer, which sizes across different service providers, is new. Although, architecture known as InterCloud \cite{BuRaCa10} investigates problem of cooperation and negotiation at cloud level, it neither has been implemented nor presented in context of autonomic system.

\subsection{Business potential}
The rapid growth of interest in cloud computing in recent years resulted in huge sums of money being invested in the field. Figure \ref{ch1:public-cloud-services-market-size} shows the size of the public cloud services market in 2012 and the forecast of its nearly two times growth in 2016. This data suggests that the subject is attractive for IT industry from the economic point of view. However, higher amounts of money spent on cloud services involve higher expectations of theirs quality from customers. Although the most significant players in cloud computing have been in the field for quite a long time, it is still possible to outline some deficiencies their products have. Additionally, lack of common standards hinder cooperation among different cloud providers. For example it is nearly impossible to create an autoscaling cloud federation with Amazon Web Services (current leader in providing cloud services\cite{GartnerMagicQuadrantSep2013}) and another provider. What is more, Amazon AWS users cannot use more lightweight virtualization methods, such as linux containers. Nevertheless, when compared to other companies especially in terms of autoscaling capabilities, Amazon really shines. OpenShift, RedHat PaaS solution, ensures application scaling but with very limited possibilities of customisation of the process -- the user can only choose if their application should scale and the whole algorithm is solely based on the number of concurrent requests to the application. Users of Heroku, another PaaS solution, have no automation tool that would control the number of instances (\emph{dynos} in Heroku nomenclature) their application is running on -- they can change it manually.
